### 2025-07-12 multiple-regression.qmd
20250712 - fix

# Compute percentile intervals for the regression coefficients
percentile_intervals <- rsample::int_pctl(boot_models, coef_info)
#percentile_intervals <- rsample::int_pctl(boot_results, results)

@@

```{r}
#| label: fig-miDensityPlot
#| fig-cap: "Histogram of Parameter Estimates Across Bootstraps."
#| fig-alt: "Histogram of Parameter Estimates Across Bootstraps."

>>>>

# Compute percentile intervals for the regression coefficients
percentile_intervals <- rsample::int_pctl(boot_models, coef_info)

@@

The distributions of the regression coefficients across boostraps are depicted in @fig-bootstrapRegressionCoefficients.

```{r}
#| label: fig-bootstrapRegressionCoefficients
#| fig-cap: "Histogram of Parameter Estimates Across Bootstraps."
#| fig-alt: "Histogram of Parameter Estimates Across Bootstraps."
